Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-07 docs/00-manuscripts/ieee/ieee-manuscript.tex
A.B. review: wording for appendix figures

\begin{figure} [ht]
	\begin{center}
		\includegraphics[width=0.48\textwidth] {correlation-filter-nri-1.pdf}
		\caption{Spearman correlation of filter rankings between various filter methods. Results of the NRI feature set are shown.}\label{fig:correlation-filters}
	\end{center}
\end{figure}

@@

\begin{figure} [ht]
	\begin{center}
		\includegraphics[width=0.48\textwidth] {correlation-nbins-1.pdf}
		\caption{Spearman correlation of filter information gain using different \texttt{\(n_{bins}\)} values for discretization of the numeric response.}\label{fig:correlation-nbins}
	\end{center}
\end{figure}

>>>>

\begin{figure} [ht]
	\begin{center}
		\includegraphics[width=0.48\textwidth] {correlation-filter-nri-1.pdf}
		\caption{Spearman correlations of NRI feature rankings obtained with different filters.}\label{fig:correlation-filters}
	\end{center}
\end{figure}

@@

\begin{figure} [ht]
	\begin{center}
		\includegraphics[width=0.48\textwidth] {correlation-nbins-1.pdf}
		\caption{Spearman correlations of rankings obtained with the information gain filter using different \texttt{\(n_{bins}\)} values for discretization of the numeric response.}\label{fig:correlation-nbins}
	\end{center}
\end{figure}
